### 2012-08-30 docs/unit_tests/unit_tests.tex
add 3-d test_projection figure

  This tests the projection routines in 2-d---either the hgprojection
  ({\tt project\_type = 1}) or the MAC projection ({\tt project\_type =
  2}).  A divergence-free velocity field is initialized and then
  ``polluted'' by adding the gradient of a scalar.  The form of the
  scalar differs depending on the boundary conditions (wall and
  periodic are supported currently).  Finally, the hgproject routine
  is called to recover the initial divergence-free field.
  Figure~\ref{fig:unit:projtest} shows the initial field, polluted
  field, and result of the projection for the hgproject case.

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of the {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity field plus
  gradient of a scalar (x-component; center); and resulting velocity after projecting
  out the non-divergence free portion (x-component; right).  This is will slipwall
  boundary conditions on all sides, a 2-level grid with the left half refined and
  right half coarse, and the hgprojection tested.}
\end{figure}

>>>>

  This tests the projection routines in 2- and 3-d---either the hgprojection
  ({\tt project\_type = 1}) or the MAC projection ({\tt project\_type =
  2}).  A divergence-free velocity field is initialized and then
  ``polluted'' by adding the gradient of a scalar.  The form of the
  scalar differs depending on the boundary conditions (wall and
  periodic are supported currently).  Finally, the hgproject routine
  is called to recover the initial divergence-free field.
  Figure~\ref{fig:unit:projtest} shows the initial field, polluted
  field, and result of the projection for the hgproject case.

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of 2-d the {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity
  field plus gradient of a scalar (x-component; center); and resulting
  velocity after projecting out the non-divergence free portion
  (x-component; right).  This is with slipwall boundary conditions on
  all sides, a 2-level grid with the left half refined and right half
  coarse, and the hgprojection tested.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=8in]{\unitfigpath/test_project_3d}
%
\caption[Results of the 3-d {\tt test\_projection} unit test]{\label{fig:unit:projtest3d}
  Projection test in 3-d showing the x-velocity (left), y-velocity
  (middle), and z-velocity (right) initially (top row), after the
  gradient of a scalar is added (center row), and the resulting
  velocity after the projection.  This is with slipwall boundary conditions
  on all sides, a 2-level grid with an octant refined, and the hgprojection.}
\end{figure}
